JavaScript as an Embedded DSL

### 2012-03-26 papers/ecoop2012/article.tex
Fixed problem with listing numbering.
Note: if you happen to have colon
in a label for your listing you need
to put it in curly braces, otherwise
latex gets confused.

Our implementation to support continuations is an example of an interesting technique of applying selective cps
transformation to embedded DSLs by means of a deep linguistic reuse, exploiting a host language feature to
implement the corresponding DSL feature without (much) additional work. An interesting insight is that CPS
transforming a program generator allows it to generate code that is in CPS.

@@

\begin{lstlisting}[label=code:cps_scala]
import java.util.{Timer,TimerTask}
val timer = new Timer
def sleep(delay: Int): Unit @suspendable = shift { k =>
  val task = new TimerTask { def run() = k() }
  timer.schedule(task, delay.toLong)
}
\end{lstlisting}

>>>>

Our implementation of continuations support is an example of an interesting technique of applying selective cps
transformation to embedded DSLs by means of a deep linguistic reuse, exploiting a host language feature to
implement the corresponding DSL feature without (much) additional work. Interesting insight is that CPS
transforming a program generator allows it to generate code that is in CPS.

@@

\begin{lstlisting}[label={code:cps_scala},caption={\code{sleep} implementation}]
import java.util.{Timer,TimerTask}
val timer = new Timer
def sleep(delay: Int): Unit @suspendable = shift { k =>
  val task = new TimerTask { def run() = k() }
  timer.schedule(task, delay.toLong)
}
\end{lstlisting}
